---
title: "Curriculum Vitae"
author: Michael C. J. Kao
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: pdf_document
---

```{r, echo = FALSE, hide = TRUE}
knitr::opts_chunk$set(echo = FALSE, hide = TRUE, message = FALSE, warning = FALSE)
```


## Personal Info
Email: mkao006@gmail.com

LinkedIn: https://www.linkedin.com/in/mkao006

Github: https://github.com/mkao006

Nationality: New Zealand/Taiwan

## Summary

This report analysis the suitability of the said individual.






```{r, load_libraries}
source("plot_functions/association_plot.R")
source("plot_functions/timeline_plot.R")
timeline_file_path = "data/timeline.json"
association_file_path = "data/association.json"
```
## Timeline

```{r, timelie_plot, fig.width=18, fig.height=12}

loaded_timeline_data = timelineDataParser(timeline_file_path)
timelinePlot(loaded_timeline_data, bar_width= 0.1)

```

It can be seen from the above graph, the individual is highly
motivated, simultneously tackling multiple tasks and constantly
learning.

## Experience

```{r, association_plot, fig.width=18, fig.height=9}

loaded_association_data = associationDataParser(association_file_path)
associationPlot(loaded_association_data)

```

From the association matrix, the individual has extensive experience
in modelling and algorithm development. He also has a descent exposure
in ETL and strategy development. Although the individual is not highly
experienced in leadership, he is poised to increase his exposure and
is not afraid of taking on additional responsibilities.

## Technical Skills

## Conclusion
